A UK Case Study on\\Cybersecurity Education and Accreditation

### 2019-06-23 FIE2019-final.tex
Final changes before submission

The work presented in this paper is a first step towards better understanding the nature, design, structure and assessment of cybersecurity education in the UK, through the lens of accreditation. It is clear that professional body accreditation is having a positive effect on universities, supporting wider national policy imperatives. We look forward to continuing this analysis, alongside other initiatives presented at the start of this paper, to provide international comparators and portability.

>>>>

The work presented in this paper is a first step towards better understanding the nature, design, structure and assessment of cybersecurity education in the UK, through the lens of accreditation. It is clear that professional body accreditation is having a positive effect on universities, supporting wider national policy imperatives. It is also clear that there is a significant need for mobilising the international computer science academic community -- alongside some of the existing initiatives presented at the start of this paper -- to continue this focus on cybersecurity education, and provide international comparators, portability and sharing of best practice.
